Sampling requirements to detect ecosystem change

### 2020-01-04 R/temporal-sampling.Rmd
moved some text to a rough draft of the manuscript

# Things to do:

- Easton: build theoretical results figure
- Sketch out figures for case studies
- Conceptual diagram 
- Begin writing - probably a shorter piece
- Possible journals: Methods Ecology and Evolution, Biological Conservation, Journal of Environmental Management, Environmental Monitoring and Assessment, BioScience,

# Introduction and setup

- Set up ideas about monitoring and cost of monitoring
- Idea of detecting change over time
- Historical data and ability to choose how much to sample
- Here, we develop a set of tools to ... We first investigate these tools using a simulated-based apporach. We then apply these tools to the detection of change points for a set of lakes...

@@

```{r theoretical_results, fig.cap='Theoretical results here',message=F,warning=F,echo=F,eval=F}

@@

par(mfrow=c(2,2))
# Sigma plot
sample_size=10

sigma15 <- param_sensitivity('sigma',15)

plot(sigma15,ylab='Probability correct',xlab='sigma',pch=16,cex.lab=1.3,las=1,ylim=c(0,1),col=1)

>>>>

@@

```{r theoretical_results, fig.cap='Theoretical results here',message=F,warning=F,echo=F,eval=T}

@@

par(mfrow=c(2,2))
# Sigma plot
sigma15 <- param_sensitivity('sigma',15)
plot(sigma15,ylab='Probability correct',xlab='sigma',pch=16,cex.lab=1.3,las=1,ylim=c(0,1),col=1)

sigma20 <- param_sensitivity('sigma',20)
points(sigma20,ylab='Probability correct',xlab='sigma',pch=15,cex.lab=1.3,las=1,ylim=c(0,1),col=3)

# phi plot
phi15 <- param_sensitivity('phi',15)
plot(phi15,ylab='Probability correct',xlab='phi',pch=16,cex.lab=1.3,las=1,ylim=c(0,1),col=1)

phi20 <- param_sensitivity('phi',20)
points(phi20,ylab='Probability correct',xlab='phi',pch=15,cex.lab=1.3,las=1,ylim=c(0,1),col=3)
